---
title: "Dashboard Texas Housing"
format: 
  dashboard:
    df-print: paged
orientation: columns
server: shiny
---


```{r}
#| context: setup
#| echo: false
#| message: false
require(dplyr)
require(ggplot2)
require(plotly)
require(tidyr)
require(shiny)

```


# Data

## column {width = 30%}

This data represents information about the housing market in Texas provided by the TAMU real estate center. The data frame contains 8602 observations and 9 variables: city Name of MLS area, year,month,date Date,sales Number of sales volume Total value of sales, median Median sale price, listings Total active listings, inventory "Months inventory": amount of time it would take to sell all current listings at current pace of sales.


```{r}
#| title: donnees txhousing
tableOutput(
 outputId = "txhousingOutputId"
)

```


# Txhousing Market

```{r}
texas <- ggplot2::txhousing

texas_sum <- txhousing %>% group_by(year,month) %>% 
  summarise(sales = sum(sales,na.rm = TRUE),
            volume = sum(volume,na.rm = TRUE),
            median = sum(median,na.rm = TRUE),
            listings = sum(listings,na.rm = TRUE),
            inventory = sum(inventory,na.rm = TRUE))

texas_sum <- texas_sum %>% ungroup()

library(lubridate)

texas_sum$date <- ymd(paste0(texas_sum$year,"-",texas_sum$month,"-1"))


# update indicator variable menu
updatemenus <- list(
  list(
    active = 0,
    x = -.125,
    type= 'buttons',
    buttons = list(
      list(
        label = "Sales",
        method = "update",
        args = list(list(visible = c(TRUE, "legendonly", "legendonly", 
                                     "legendonly", "legendonly" )))),
      list(
        label = "Volume",
        method = "update",
        args = list(list(visible = c("legendonly", TRUE, "legendonly", 
                                     "legendonly", "legendonly")))),
      list(
        label = "Median",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", TRUE, 
                                     "legendonly", "legendonly")))),
      list(
        label = "Listings",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", "legendonly", 
                                     TRUE, "legendonly")))),      
      list(
        label = "Inventory",
        method = "update",
        args = list(list(visible = c("legendonly", "legendonly", "legendonly", 
                                     "legendonly", TRUE))))
    )
  )
)

p11 <- plot_ly(data = texas_sum) %>% 
  
  add_lines(x=~date, y=~sales, name = "Sales", visible = "TRUE") %>%
  add_lines(x=~date, y=~volume, name = "Volume", visible = "legendonly") %>%
  add_lines(x=~date, y=~median, name = "Median", visible = "legendonly") %>%
  add_lines(x=~date, y=~listings, name = "Listings", visible = "legendonly") %>%
  add_lines(x=~date, y=~inventory, name = "Inventory", visible = "legendonly") %>%
  
  layout(title = "Texas Housing Market Time Series", showlegend=TRUE,
         xaxis=list(zeroline = FALSE,title="Date"),
         yaxis=list(zeroline = FALSE,title="Value"),
         updatemenus=updatemenus)

p11
```


# Tendence Annuel

## Sidebar {.sidebar}

```{r}
selectInput(
 inputId =  "variableInputId",
  label = "variable",
  choices = c('sales','median','listings','inventory')
)
```


```{r}
require(ggplot2)
selectInput(inputId = 'yearinputid2',label = 'year',choices = unique(txhousing['year']))

```


## row

```{r}
#| title: tendence annuel pour une variable choisie 
plotlyOutput("yearoutput")
```



# Tendence mensuel 

## Sidebar {.sidebar}

```{r}
selectInput(
 inputId =  "variableInputId",
  label = "variable",
  choices = c('sales','median','listings','inventory')
)
```

```{r}
selectInput(inputId = "monthinputid2",label = "month",choices = unique(txhousing$month))
```

## row

```{r}
#| title: evolution mensuelle 
plotlyOutput("monthoutput")
```


# Graphic


## Sidebar {.sidebar}


```{r}
selectInput(
 inputId =  "variableInputId",
  label = "variable",
  choices = c('sales','median','listings','inventory')
)
```

## row

```{r}
plotlyOutput(
  outputId = "histogramOutputId"
)

plotOutput(
  outputId = "lineOutputId"
)

```

## row

```{r}
plotlyOutput(
outputId= "boxplotOutputId"
)
```



# Analyse bivariee 

## Sidebar {.sidebar}


```{r}
selectInput(
 inputId =  "XInputId",
  label = "X",
  choices = c('sales','median','listings','inventory')
)
```


```{r}
selectInput(
 inputId =  "YInputId",
  label = "Y",
  choices = c('sales','median','listings','inventory')
)
```


##

```{r}
plotlyOutput(
outputId= "cityOutputId"
)

```
##


```{r}
plotlyOutput(
outputId= "scaterOutputId"
)
```











```{r}
#| context: server

output$txhousingOutputId <- renderTable(
  {
    txhousing%>%
      head()
  }
)

output$histogramOutputId <- renderPlotly({
  variable = input$variableInputId
  
  (txhousing %>%
    ggplot(mapping = aes(x = !!rlang::sym(variable))) +
    geom_histogram(fill = "blue")
)%>%
    ggplotly()
  
}
)


output$lineOutputId <- renderPlot({
  
  variable = input$variableInputId
data = txhousing %>%
   group_by(year) %>%
   summarise(
    Y= sum(!!rlang::sym(variable),na.rm = TRUE),
    )
ggplot(data, aes(x = year, y = Y))+
  geom_line(color = "coral", size = 1) +
  geom_point(color = "black")+
  theme_minimal()+
  labs(title = "tendence des variables  entre 2000 et 2015")
})


output$boxplotOutputId <- renderPlotly({
  
  variable = input$variableInputId

( 
ggplot(txhousing, aes(x=factor(month), y=!!rlang::sym(variable))) + 
  geom_boxplot(aes(color = 'blue'))
)%>%
  ggplotly()
}
)

#bivarié

output$cityOutputId <- renderPlotly({
  
  variable = input$XInputId
  variable1= input$YInputId

(txhousing %>%
  filter(year == 2005, month == 7) %>%
  filter(!is.na(sales), !is.na(median)) %>%
  ggplot(aes(x= !!rlang::sym(variable), y=!!rlang::sym(variable1),label = city)) +
  geom_point() +
  geom_text(nudge_y = 4000, size = 3) +
  scale_x_log10() +
  theme_minimal()
)%>%
  ggplotly()
}
)




output$scaterOutputId <- renderPlotly({
  
  variable = input$XInputId
  variable1= input$YInputId

(
  ggplot(txhousing, aes(x=!!rlang::sym(variable), y=!!rlang::sym(variable1))) + 
geom_point(aes(color="blue"))
)%>%
  ggplotly()
}
)


output$yearoutput <-renderPlotly( 
  {
    var = input$variableInputId 
    annee=input$yearinputid2
   ( txhousing%>%
       filter(year==annee)%>%
      dplyr::group_by(month)%>%
      dplyr::summarise(
        variable_choisie=sum(!!rlang::sym(var) ,na.rm = TRUE)
      )%>%
      ggplot(mapping = aes(x=month,y=variable_choisie))+
      geom_point(color= 'black')+
      geom_line(color='coral')+
      theme_minimal()
)%>%
      ggplotly()
  }
)
  

output$monthoutput <- renderPlotly(
  
  {
    var = input$variableInputId 
    mois=input$monthinputid2
    (txhousing%>%
      dplyr::filter(month==mois)%>%
      group_by(year)%>%
      summarise(
        variable_choisie=sum(!!rlang::sym(var),na.rm = TRUE)
      )%>%
      ggplot(mapping = aes(x=year,y=variable_choisie))+
        geom_point(color='black')+
        geom_line(color='blue')
    )%>%
      ggplotly()
  }
)




```
                                    



